\chapter{Introduction}

% Last updated: 20201022

This short book is all about how I won \$10,000 in ten weeks of poker
playing. In the Computer Programming world there's a famous book from
2010 called ``Seven Languages in Seven Weeks'', where seven
programming languages are presented to give you a meaningful taste of
all of them. The languages are Clojure, Haskell, Io, Prolog, Scala,
Erlang and Ruby. I've borrowed the name of that book for this new
standalone poker book, Ten Thousand in Ten Weeks.

Some of this book has appeared in my last three Lessons From Sessions
reports, ``Winter 2019'' (12th Sept 2019), ``Running Hot'' (19th Sept
2019) and ``Early October'' (10th Oct 2019). If you're not a Lessons
From Sessions reader, send me an email and I'll send you those reports
and future Lessons From Sessions. You don't need to read those reports
to appreciate this book, I've duplicated information as necessary and
this book is standalone.

% \section*{name} : an unnumbered section that won't appear in the contents
\section*{A Ten Week Spring campaign}

Racehorses don't race every Saturday. They enter a few races, racing
once a fortnight or so, and every so often have a break of 30 days or
more. You can't flog a dead horse, and horses need a break (this is
indicated in form guides with the word Spell). The horse's group of
races are called a \textbf{campaign}, in the first race the horse is
``first-up'', in the next race he is ``second-up'' and so on.

As a poker player I don't play every day and I enjoy a week off here
and there; typically when real-world commitments prevent me from
playing my favourite games. I can start or finish a campaign whenever
I like; it's just a start and finish time for a series of session
results. After a breakthrough win at a \$250 Pot Limit Omaha Sit and
Go, I started winning in most of my sessions and felt that I was in
the middle of an excellent campaign.

I'm now finishing my Spring 2019 Campaign with the publication of this
book. My Summer 2019 Campaign starts Friday 25th October, with a trip
to Casino Canberra for their 1/2/5 or 5/5 PLO game.

\section*{Significant Sessions}

% FIXME: check the number of significant sessions in the final copy
% 12? 13? 11??

There are twelve significant sessions in the campaign covered in this
book. A \textbf{significant session} is a poker game where I've
committed two hundred dollars or more. If I play a \$22 pub game with
a \$250 first prize, that game cannot be a significant session; the
money isn't big enough to care about and won't affect my final
result. I didn't play any games of that size in Spring 2019. There
were two games I played that did not reach significant status. Both
were 1/1 PLO cash games. In the first game (at Lakes) I was in for
\$150 and cashed out for \$190, winning \$40, in the second game I was
in for \$150 and cashed out for \$110, losing \$40. Those two results
cancel each other out and I won't include them in this book.

% FIXME: but quickly discuss them?

\section{How to win \$10,000 at poker}

The easiest way of winning \$10,000 at poker is to get lucky in a
single big tournament. Indeed I was at the final table of a 100+
player, \$250 buyin tournament in August, where the first prize was a
guaranteed \$10,000. Because the first prize was guaranteed to be 10k,
that tournament had a very top-heavy payout structure. I finished
fourth for \$950.



%% \section*{About the author}

% FIXME: Back cover copy?

%% Stuart Cooper wrote the ``Doctor Straight'' column, primarily
%% on Pub Poker Tournaments, in the Australian Poker Weekly newspaper
%% for the entirety of the newspaper's two-and-a-half year run.
%% In the 131 issues of the paper he produced 105 columns.

%% Stuart has three major tournament wins (50\$ buyin, 100+ players)
%% to his credit and many small nightly tournament wins.

%% He lives and plays poker in Sydney.
