\chapter{Professional Poker}

Are you a poker professional? If you've got no other major income and
you're making money primarily through poker, then you're a
professional. For the Spring Campaign of 2019, I was a poker
professional. This chapter covers aspects of playing poker as a pro.

\section*{Keep your expenses down}

You don't want to go through life as a tightwad but you don't want to
go wasting your money either. It's a fine line. One thing I always do
that saves me \$40 or so is book my Sydney Airport Carparking at the
cheaper carpark that's a ten minute walk away from the
terminal. In effect I pay myself \$2 a minute for a 10 minute walk
each way. It's nice to get paid for walking. My trip to Crown ended up
being expensive nonetheless because I didn't book the tickets until
the day before Ihad to fly; that was quite annoying and my Crown
winnings of a bit under \$900 didn't cover the cost of the trip, but
any winnings are good winnings. I'll be going to Crown in the second
week of November, and booking my flights and parking well in advance.

Canberra trips incur expenses of petrol and often one night's hotel,
but a tank of petrol for my car is about \$70 and a night's hotel at
a very good hotel can be under \$150. Since I've been winning about
\$2,000 at each Canberra session, the expenses are about 10\% of
the win.

I'm no expert on hotels but I will say that if you stay at the Deco
Hotel in Northboure Avenue, you're very unlikely to be disappointed.

\section*{Game selection}

I didn't play very often in this campaign, sixteen sessions in ten
weeks which doesn't even work out to twice a week. Obviously the
Petersham 250 Sit and Go is a staple of my calendar now and the
Canberra trips are important when I can fit them in.

There was a big St John's Park \$660 No Limit Holdem Tournament Main
Event at the end of the campaign that I considered playing in, but
passed on. Like Rounders Club, St Johns Park Bowling Club is
a venue that I've never done well at.

\section*{The Summer 2019 Campaign}

My summer campaign starts tonight with a drive to Canberra for their
big PLO cash game. I've got some weeks off in November so I'll make
another trip to Crown. I expect the No Limit Holdem Tournament scene
to quieten down during December as people go on holidays and the
Christmas scene takes hold. For calendar convenience this campaign
lasts from Friday 25th October until Tuesday 31st December.

I'll give myself a bigger budget for this campaign, a bank of
\$8,000. This is my reward for my excellent Spring Campaign. I'd like
to double that money in the campaign, so my win target for the eleven
weeks is \$8,000 at a bit under \$800 a week.
