\chapter{Every session}

\section*{PSH1: Petersham \$250 PLO Sit and Go}

This is a fortnightly game played on Thursday nights at Petersham.
I played it four times in the Spring Campaign for an agreed first,
a split-first, a split-first and a seventh. The games are sessions
PSH1, PSH2, PSH3 and PSH5.

The buyin is \$250 and there's a dealer provided, so it's \$220 to
the prize pool and \$30 to the house. The game has a solid core of
8 or 9 players, and the game is played under ``spare stack''
conditions. Spare Stack means that if fewer than 10 people are playing
that night, rebuys are allowed until 10 stacks have been sold.

Some of the players in the game have more money than (poker) sense and
are happy to take early chances and re-buy for another \$250 if they
bust and the rebuy option is still available. I'm happy to take just a
single shot; especially since the game has a generous starting stack
of 100,000 and you don't have to get involved in big confrontations
early on if you don't want to.

This game normally ends up with 11 entries in the prizepool and pays
first place \$1520 and second place \$900 (first gets 63\% second gets
37\% this seems a fair split).

In this game I was about a 85\% chip leader and did a handshake deal
with the second place finisher that I was the winner and instead of a
1520/900 split we'd do 1400/1000 with a bonus \$20 tip to the
dealer. Second place was very happy to take this deal and I was that
night's winner and up \$1,150 for my night's work.

\section*{MCN1: Marconi \$330 PLO with Rebuys}

Big Pot Limit Omaha tournaments are rare as hen's teeth. There's
probably only 10 PLO tournaments of \$300+ buyins in the Sydney
Pub/Club scene every year and you don't find that many at The Star or
Crown Melbourne either; they typically turn up only in quarterly event
series.

So I normally make an effort to play a bigger PLO game; this game was
on a Monday night where I normally play social cards at Parramatta RSL
club; I play social cards probably 9 weeks out of 10 but I do cancel
occasionally when there's another event on and a Marconi PLO
tournament qualified as another event.

This game is by far the smallest result of my Spring Sessions (+\$10!)
but one of the most important because it was a rebuy tournament and
I'd rebought twice and was invested for \$990!!. The game paid down to
five players and my fourth placing got me \$1000 for the smallest of
profits.

It's better to win a tiny \$10 than to lose an enormous \$990 so this
result is one of the most important of my Spring Sessions. Indeed,
this was the session where I had the most money invested.

The same game is being played next Monday, 28th October. I'm not as
keen to play it this time around (I don't like being stuck a grand in
a tournament) so I'll just see how I feel on the day.

\section*{CCA1: Casino Canberra 1/2/5 PLO Cash \$200-unlimited buyin}


