\chapter{The Sessions}

Here is the list of significant sessions covered by this book. The
campaign starts with a bankroll of \$5,000; the ``Bank'' column shows
the resulting bankroll after each session. My poker bankroll is much
bigger than \$5,000 but it's a good idea to think of \$5,000 as my
campaign budget. \$5,000 is \$500 a week to spend on poker in a ten
week campaign. If I burn through that money, I should stop the
campaign and take a spell from poker before launching a new campaign.

\begin{tabular}{rlrllrr}
 Game & Ref & Date & Venue & Game Structure & Result & Bank \\
     &           &      &           &             &       & \$5000 \\
  1  &   PSH1    & 15/8 & Petersham & 250 PLO SNG & (1st) +1150 & 6150 \\
  2  &   MCN1    & 26/8 & Bossley Park & 330 PLO rebuys & (4th)~~~+10 & 6160 \\
  3  &   CCA1    & 31/8 & Canberra  & 1/2/5 PLO 200+ & +2775 & 8935 \\
  4  &   PSH2    & 12/9 & Petersham & 250 PLO SNG & (eq 1st) +950 & 9885 \\
  5  &   CCA2    & 13/9 & Canberra  & 1/2/5 PLO 200+ & +1575 & 11460 \\
  6  &   LAK1    & 15/9 & Lakes Hotel & 1/1 PLO 50-100 & -660 & 10800 \\
  7  &   LAK2    & 22/9 & Lakes Hotel & 1/1 PLO 50-100 & +200 & 11000 \\
  8  &   PSH3    & 26/9 & Petersham & 250 PLO SNG & (eq 1st) +950 & 11950 \\
  9  &   CWN1    & 2/10 & Crown Melb & 5/5 PLO 1/3 PLO & +870 & 12820 \\
 10  &   RND1    & 4/10 & Five Dock & 200 NLHT & (4th) +900 & 13720 \\
 11  &   PSH4    & 7/10 & Petersham & 250 NLHT & -150 & 13570 \\
 12  &   PSH5    & 10/10 & Petersham & 250 PLO SNG & -250 & 13320 \\
 13  &   CCA3    & 11/10 & Canberra  & 5/5 PLO 200-2000 & +2020 & 15340 \\
 14  &   RND2    & 18/10 & Five Dock & 200 NLHT & -200 & 15140 \\
     &           &       &           & TOTALS & +10,140 & \$15,140 \\
\end{tabular}

I write about each session later in the book; you may want to
refer back to this table regularly. A quick note on Session 11 (PSH4): I had
a ``\$100 off the \$250 entry fee'' ticket from having done well in
their previous big \$250 game; so although I busted out early the \$250
game only did \$150 damage to the Bank. The two tournaments I came
Fourth in (MCN1 and RND1) had fourth prize of about \$1,000 and first
prize of about \$3,500.

\section*{Calendar of Sessions}

\begin{tabular}{rrrrrrrrr}
  Week & Starting & Mon & Tue & Wed & Thu & Fri & Sat & Sun \\
  1 & 12/8  &     &     &     & PSH1 &     &     &     \\
  2 & 19/8  &     &     &     &      &     &     &     \\
  3 & 26/8  & MCN1 &    &     &      &     & CCA1 &    \\
  4 & 2/9  &      &    &     &      &     &     &     \\
  5 &  9/9  &     &     &     & PSH2 & CCA2&     & LAK1\\
  6 & 16/9  &     &     &     &      &     &     & LAK2\\
  7 & 23/9  &     &     &     & PSH3 &     &     &     \\
  8 & 30/9  &     &     & CWN1&      & RND1&     &     \\
  9 & 7/10 & PSH4 &    &     & PSH5 & CCA3&     &     \\
 10 & 14/10 &     &     &     &      & RND2&     &     \\
\end{tabular}

You can see the fortnightly Thursday Petersham \$250 PLO Sit and Gos
on the calendar. My Canberra trips are either for Friday night or
Saturday night, sometimes both. PLO doesn't always get up on other
nights and I've got business in Sydney on Mondays and Thursdays so
Friday and Saturday nights are easily the best for Canberra PLO. I
am enjoying horseracing more and more and the big race days are always
Saturday afternoons so Canberra trips normally knock off my racing
plans. Still it's better to win \$2,000 at Canberra than it is to win
or lose \$150 at the races. Plus Canberra have racedays on some Friday
afternoons so I can often combine a Friday night Casino visit with a
few hours at the Canberra track earlier that day.

MCN1 and PSH4 sessions were one off events, I don't typically play
poker on Mondays. The Lakes Hotel game is played every Sunday night.

I almost never play poker on Saturday nights.
